---
title: "ECON 3880: Assignment 1"
author: "Iman Ullah and Kunwar Nir" 

date: '`r Sys.Date()`'
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
    df_print: paged
    number_sections: true
---
Do not change anything above this line except your name, even a single space!


# Q1:

Question 1 goes here.

```{r}
# Write your code here to answer Q1. For example I have added 2 lines of code to this code chunk
install.packages("ggplot2")
library(ggplot2)
df <- read.csv('insurance.csv')
ggplot(data = df, aes(x = region, fill = sex)) +
  geom_bar() +
  labs(title = "Count Plot of Observations by Region and Sex",
       x = "Region",
       y = "Count")
```

Here you will type the answer to the Q1, if need be. 

# Q2:

Question 2 here.

```{r}
# Your code here
ggplot(data =df, aes(x = bmi, y = charges, color = smoker)) +
  geom_point() +
  geom_smooth( method = lm) + 
  labs(title = " The link between BMI and Charges: Smokers and nonsmokers.",
       x = "Body Mass Index",
       y = "Dollar Charged",
       color = "Smoker")
  
  "Conclusion: there is a positive correlation between BMI and charges for smokers"
```
Your answer to Q2 here.
Conclusion: there is a positive correlation between BMI and charges for smokers
 
# Q3:

Question 3 here.

```{r}
# Your code here to answer Q3
ggplot(data = df, aes(x = region, fill = smoker)) +
  geom_bar(position = "stack") +
  coord_flip() +
  theme_minimal() +
  geom_text(stat = "count", aes(label = ..count..), position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Stacked Bar Chart of Smokers and Non-Smokers by Region",
       x = "Region",
       y = "Count",
       fill = "Smoker")
```

Your answer to Q3 here.


# Q4:

Question 4 here.

```{r}
# Your code here
library(plotly)
plot_ly(data = df, x = ~bmi, y = ~charges, color = ~region, type = 'scatter', mode = 'markers')
  layout(title = "Interactive Scatter Plot of BMI vs Charges",
         xaxis = list(title = "BMI"),
         yaxis = list(title = "Charges"))
```

Your answer to Q4 here.


Also remember that you need to run all the code chunks and then save the file before clicking on Preview. After clicking on Preview, RStudio will save a file in your computer with an extension of *nb.html*; for example, **Assignment1.nb.html**, which you will send it to me.

***Good luck!***


