---
title: "ECON 3880: Assignment 3"
author: "Iman Ullah and Kunwar Nir" 

date: '`r Sys.Date()`'
output: 
  html_notebook: 
    toc: yes
    toc_float: yes
    df_print: paged
    number_sections: true
---
Do not change anything above this line except your name, even a single space!


# Q1:

Question 1 goes here.

```{r}
library(tidyverse)
syr <- read_rds('SYRflights2021.rds')
first_three_rows <- head(syr, 3)
print(first_three_rows)
```

Here you will type the answer to the Q1, if need be. 

# Q2:

Question 2 here.

```{r}
str(syr)
```
We have a bunch of int, num, chr and POSIXct

Your answer to Q2 here.
 
# Q3:

Question 3 here.

```{r}
nyc_flights <- syr |>
  filter(arr_delay > 300, dest %in% c("JFK", "LGA", "EWR"))
print(nyc_flights)

```
There are 9 flights which match those conditions

Your answer to Q3 here.


# Q4:

Question 4 here.

```{r}
syr <- syr |>
  mutate(distance_km1 = distance * 1.61)
syr$distance_km2 <- syr$distance * 1.61
df_new <- syr |>
  select(MONTH = month, carrier, distance_km1, distance_km2, ends_with("time"))
tail(df_new, 4)
```

Your answer to Q4 here.


Also remember that you need to run all the code chunks and then save the file before clicking on Preview. After clicking on Preview, RStudio will save a file in your computer with an extension of *nb.html*; for example, **Assignment1.nb.html**, which you will send it to me.

***Good luck!***



